Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-09-01 manuscript/draft.Rmd

Forecasts describe how systems are expected to change through time. While some
areas of ecological forecasting focus primarily on time-series data, others
primarily focus on using spatial models and space-for-time substitutions. Using
ecological and environmental time-series data allows the consideration of actual
dynamics from both a process and error structure perspective [@tredennick2016].

>>>>

Forecasts describe how systems are expected to change through time. While some
areas of ecological forecasting focus primarily on time-series data [@ward2014], 
others primarily focus on using spatial models and space-for-time substitutions
[@blois2013]. Using ecological and environmental time-series data allows the
consideration of actual dynamics from both a process and error structure
perspective [@tredennick2016].
